Response to reviewers

### 2022-05-05 response/response2.Rmd
responses all sorted

The editor mention that while the data are interesting, the necessary details for a pedagogical application or case study are still largely missing. The manuscript reads more like a paper about the R package, something for a software journal.

The editor agree with the general sentiment among two of three reviewers that this paper is improved over the previous version, but still does not make clear contributions to educators other than its use in class. If this was (1) a general process for demonstrating the cleaning of longitudinal data, (2) a case study for cleaning data in the classroom, or (3) a case study for using the data in the classroom the value would be clear. In its current state, however, the manuscript still partly each of the three by describing the R package they’ve created and, as a result, does not  fully address any of the three.

\begin{description}
\item[Associate Editor:] \textcolor{violet}{\textbf{The author switches between gender (man/woman/etc) and sex (male/female/etc.) throughout the manuscript. Further, the explanation here covers important ideas in teaching how to use data on gender/sex and race, but it’s just the beginning of ideas. It might be better to discuss the questions on the survey and discuss possible shortcomings, rather than make a somewhat empty gesture towards today’s standard.} The authors still incorrectly refer to male/female as gender. While it is clear the authors are trying to be thoughtful in how they address important issues with data collection on demographics they are not correctly doing so (see note about race/ethnicity below). Certainly there are potential issues with binary sex variables, this can and should be discussed but care should go into this. Please review the literature surrounding the discussion of sex and gender in data (e.g., SAGER guidelines).}
\end{description}

@@

@@

@@

\begin{description}
\item[Associate Editor:] \textcolor{violet}{The authors also make some problematic decisions about the race (Black or not-Black) and ethnicity (Hispanic or not-Hispanic) variables. They suggest three categories (non-Black/non- Hispanic; Black; Hispanic) and don’t discuss the process of combining them, while recent stan- dard is (non-Black/non-Hispanic; non-Black/Hispanic; Black/non-Hispanic; Black/Hispanic). It’s possible that this selection was made for backwards compatibility, lack of certain demo- graphics in the sample, or some other reason but it is not communicated. Please review the literature surrounding the discussion of race and ethnicity (e.g., Standards for the classifica- tion of federal data on race and ethnicity).}
\end{description}

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

* All of the comments on the list above have been addressed. (**Except for the Cooksey reference**)

@@

>>>>

The editor says \textcolor{violet}{The paper falls squarely into the call for the special issue on `Reproducibility and responsible workflow". Some additional suggestions regarding framing are provided by the reviewers and the AE.} The only comments on framing appear to come from the associate editor: \textcolor{violet}{If this was (1) a general process for demonstrating the cleaning of longitudinal data, (2) a case study for cleaning data in the classroom, or (3) a case study for using the data in the classroom the value would be clear. In its current state, however, the manuscript still partly each of the three by describing the R package they've created and, as a result, does not  fully address any of the three.}

We would argue that the current form of the paper is clearly (2), and we have added some wording in the introduction and lesson learned sections to help make this clear. XXX DC to do

\begin{description}
\item[Associate Editor:] \textcolor{violet}{\textbf{ORIGINAL COMMENT: The author switches between gender (man/woman/etc) and sex (male/female/etc.) throughout the manuscript. Further, the explanation here covers important ideas in teaching how to use data on gender/sex and race, but it’s just the beginning of ideas. It might be better to discuss the questions on the survey and discuss possible shortcomings, rather than make a somewhat empty gesture towards today’s standard.} R1 COMMENT: The authors still incorrectly refer to male/female as gender. While it is clear the authors are trying to be thoughtful in how they address important issues with data collection on demographics they are not correctly doing so (see note about race/ethnicity below). Certainly there are potential issues with binary sex variables, this can and should be discussed but care should go into this. Please review the literature surrounding the discussion of sex and gender in data (e.g., SAGER guidelines).}
\end{description}

We interpret this to mean we should change the variable name in the cleaned data, and so have done this, and then "sex" is uniformly used throughout the paper. XXX Dewi to do

@@

We have added more explanation of the two variables, and suggestions of where to use one vd the other in classroom analyses. XXX Dewi to do

@@

Using `rlm` with the `nest` and `map` functions from `tidyr`, efficiently and simply fit these models, and are easy to explain in a classroom setting. Similar result would result from using robustlmm, but it avoids memory and fitting issues. We have added more words to the text to explain this. XXX DC to do

@@

This is more of a comment than a request to make a change, but we agree that this is an area that could be a good classroom discussion. We have added a couple of additional sentences to highlight the richness of this topic, and alternative approaches that might be explored. XXX DC to do

\begin{description}
\item[Associate Editor:] \textcolor{violet}{The authors also make some problematic decisions about the race (Black or not-Black) and ethnicity (Hispanic or not-Hispanic) variables. They suggest three categories (non-Black/non-Hispanic; Black; Hispanic) and don’t discuss the process of combining them, while recent standard is (non-Black/non-Hispanic; non-Black/Hispanic; Black/non-Hispanic; Black/Hispanic). It's possible that this selection was made for backwards compatibility, lack of certain demographics in the sample, or some other reason but it is not communicated. Please review the literature surrounding the discussion of race and ethnicity (e.g., Standards for the classification of federal data on race and ethnicity).}
\end{description}

It would be nice if the database contained a broader description of race, but it only has a single variable for race. For this reason, our cleaned data reflects this, and has a single variable for race. XXX Dewi to do

@@

XXX DC to do

@@

We think it is best to keep this emphasis, because the hard work is on cleaning and tidying the data, in a reproducible manner, which is close to the mission of the special issue. We have added some additional sentences about lessons for statistics and data science educators. XXX DC to do (might need help from Emi or Nick)

@@

We have changed all to "refresh". XXX Dewi

@@

Thanks for this, exactly right! We have changed the wording accordingly. XXX DC

@@

Same point as made by the AE, and how we have addressed it is described above.

@@

XXX DC to address

@@

Done XXX Dewi

@@

XXX Dewi Add some words to make it clear what data this is summarising

@@

We have expanded this explanation XXX Dewi

@@

@@

We have put the capitalisation back in, and changed "WHITE" to be "NBH". XXX Dewi
